---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lm.fit.and.graph

<!-- badges: start -->
<!-- badges: end -->

The goal of the lm.fit.and.graph package is to summarize and plot the linear relationship between 2 variables in a data set. It provides a linear model and a scatter plot fitted to the 2 variables that the user can specify. 

## Installation

The current function is not yet available on CRAN. 

The development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2021/functions-britttheuser")
```
## Example

The following is an example application package using 2 variables (concave points mean and concavity mean) from the Cancer sample dataset. 

```{r example}
library(lm.fit.and.graph)
correlation_lm_and_plot(datateachr::cancer_sample, datateachr::cancer_sample$concave_points_mean, datateachr::cancer_sample$concavity_mean)
```

